Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-06 CVPR16/Source/abstract.tex
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

\begin{abstract}

We present a physically interpretable, continuous 3D model for handling occlusions with applications to road scene understanding. We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray. Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion point tracks with potentially occluded objects or modeling object detection scores in applications such as 3D localization. For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM. Detailed experiments on the KITTI dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions. We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.

>>>>

\begin{abstract}
We present a physically interpretable, continuous three-dimensional (3D) model for handling occlusions with applications to road scene understanding. We probabilistically assign each point in space to an object with a theoretical modeling of the reflection and transmission probabilities for the corresponding camera ray. Our modeling is unified in handling occlusions across a variety of scenarios, such as associating structure from motion (SFM) point tracks with potentially occluding objects or modeling object detection scores in applications such as 3D localization. For point track association, our model uniformly handles static and dynamic objects, which is an advantage over motion segmentation approaches traditionally used in multibody SFM. Detailed experiments on the KITTI raw dataset show the superiority of the proposed method over both state-of-the-art motion segmentation and a baseline that heuristically uses detection bounding boxes for resolving occlusions. We also demonstrate how our continuous occlusion model may be applied to the task of 3D localization in road scenes.

### 2016-04-06 CVPR16/Source/applications.tex
Fixed Equation (15) (19) and the summation over dynamic and size.
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2

In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using objects and point tracks.

@@

Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error. When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z$ is the normalization coefficient.

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z'$ is the new normalization coefficient.

@@

In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and background if outside all bounding boxes). For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes. As we demonstrate in our experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} from our occlusion model.

@@

We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -Z 
   + \sum_{t=s_i}^{e_i} \lambda_t\EnergyTrack
  + 
  \sum_{t=s_i}^{e_i}
  \sum_{i=1}^N  
  %\sum_{\substack{i \in [1, \dots, N] \\t \in [s_i, \dots e_i]}}
  \lambda_d\EnergyBBox
  + \lambda_{\text{dyn}}\EnergyDyn
  + \lambda_{\text{size}}\EnergySize
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{t}$, $\lambda_{d}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$ and $Z$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modelling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

\begin{figure}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each car are modeled as random variables. (Bottom) Graphical model for a single frame. The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables (detection bounding boxes and point tracks), while the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{figure}

\vspace{-0.3cm}
\paragraph{Continuous point tracks energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with the object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model. Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function. We choose this over alternatives such as block coordinate descent since they are slower in our experiments.

>>>>

In this section, we highlight the versatility of our occlusion modeling by demonstrating its unified application to two different problems: associating point tracks with objects and 3D object localization using objects and point tracks. Table~\ref{tab:notations} summarizes inputs and outputs for these problems.

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Est. by~\cite{Song_Chandraker_2014} for initialization}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

@@

Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error. When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z'}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z'$ is the normalization coefficient.

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z"}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z"$ is the new normalization coefficient.

@@

In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and the background if outside all bounding boxes). For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes. As we demonstrate in our experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} from our occlusion model.

@@

We exploit in this section the application of our continuous occlusion model to 3D object localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -\tilde{Z} 
  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
  + \\ 
  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
  \left(
    \lambda_{\text{detect}}\EnergyBBox
    + \lambda_{\text{dyn}}\EnergyDyn    
    + \lambda_{\text{size}}\EnergySize
  \right)
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modeling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

\begin{figure}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables. (Bottom) The graphical model corresponding to the above frame. In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{figure}

\vspace{-0.3cm}
\paragraph{Continuous point track energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates (computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera). We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa. Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{multline}
where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model. Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function. We choose this over alternatives such as block-coordinate descent since they are slower in our experiments.

### 2016-04-06 CVPR16/Source/contBBoxModel.tex
Addressed other comments from R24. (1) Added one of the references (2) take -> taken (3) Explained how we get the number of cars from detections (4) Added statistics about KITTI dataset (5) Clarified that we use Song and Chandrakar 2014 for initializing 3D location and sizes as well. (6) Added baselines to experiment table (7) Added one line explanation of the baselines (8) Clarified the Lambertian reflection line (9) summer -> sum
Make symbols consistent, Include most of reviewer comments (except for related works by Reviewer 2, Proof reading

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$ as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u) \enspace .
\end{align}

If a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in detection score is given by 
  $\Lambda'_k = \mathcal{P}_{i} + \Lambda_k$ for all $k$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{'-1} \bepsilon_k^{i}(t) \right)
\end{multline}

The energy of detection scores is simply take to be the inverse of the detection score.
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}
\end{align}

>>>>

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is usually not desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of our proposed detection bounding box is known to be
occluded, we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundaries of the detection bounding box, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$ where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix in the detection score is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix as follows
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

The energy of detection scores is simply taken to be the inverse of the detection score as
\begin{align}
  \Energy{detect}(\{ \relp{i}{t} \}_i, \{\dimsn{i}\}_i ) = \frac{1}{S'(\bb{i})}.
\end{align}
